{\pkg}: A Python Package for Integrating Computational Models Across Languages and Scales

### 2019-02-01 papers/lang2018/ms.tex
Change names but don't remove todo flags

%---------------------------------------------------------------------------------
% CONTROL THINGS
\newcommand{\todo}[1]{{\color{red}{#1}}}
\newcommand{\addref}{{\color{red}(ref. needed)}}
\newcommand{\Msol}{\,M$_{\odot}$}
\newcommand{\TB}{\,Tbytes}
\newcommand{\pkg}{{\tt yggdrasil}{}}
\newcommand{\cis}{{\tt cis\_interface}{}}
\newcommand{\pkglink}{\todo{cis\_interface}}
%\newcommand{\pkg}{{\tt \todo{cis\_interface}}{}}
\newcommand{\pkgrun}{{\tt yggrun}}
\newcommand{\A}{Appendix{ }}
\newcommand{\hrefgit}[1]{\href{https://github.com/cropsinsilico/cis_interface}{\todo{#1}}}
\newcommand{\hrefdoc}[1]{\href{https://cropsinsilico.github.io/cis_interface/}{\todo{#1}}}
\newcommand{\hrefhack}[1]{\href{https://cropsinsilico.github.io/cis_interface/hackathon2018/index.html}{\todo{#1}}}

@@

We present an Open Source Python package, {\pkg}, for creating and running integration networks by connecting existing computational models written in different programming languages. {\pkg} was developed as part of the Crops \emph{in Silico} \citep{Marshall-Colon2017} initiative to build a complete crop \emph{in silico} from the level of the genes to the level of the field. {\pkg} is available on Github\footnote{{\tt https://github.com/cropsinsilico/\pkglink}} with full documentation\footnote{{\tt https://cropsinsilico.github.io/\pkglink/}} and can be installed from PyPI\footnote{{\tt https://pypi.org/project/\pkglink/}} via \todo{\tt pip install {\pkg}} or conda-forge\footnote{{\tt https://github.com/conda-forge/\pkglink-feedstock}} via \todo{\tt conda -c conda-forge install {\pkg}}. Although developed for the purpose of integrating plant biology models, {\pkg} can be applied to any situation requiring coordination between models in the supported languages. \S\ref{S:background} provides background information on existing efforts for cross-language model integration, \S\ref{S:methods} describes the methods used by the {\pkg} package to integrate models, \S\ref{S:example} provides a worked example of integrating the two model presented above, \S\ref{S:results} presents several tests demonstrating the performance of message passing between integrated models, and \S\ref{S:discuss} describes a few use cases for {\pkg}, 
summarizes the features and limitations of the {\pkg} package, and outlines areas of ongoing and future development.

>>>>

%---------------------------------------------------------------------------------
% CONTROL THINGS
\newcommand{\todo}[1]{{\color{red}{#1}}}
\newcommand{\addref}{{\color{red}(ref. needed)}}
\newcommand{\Msol}{\,M$_{\odot}$}
\newcommand{\TB}{\,Tbytes}
\newcommand{\pippkg}{\todo{\tt yggdrasil-framework}}
\newcommand{\condapkg}{\todo{\tt yggdrasil}}
\newcommand{\pkg}{{\tt yggdrasil}{}}
\newcommand{\cis}{{\tt cis\_interface}{}}
\newcommand{\pkglink}{\todo{cis\_interface}}
%\newcommand{\pkg}{{\tt \todo{cis\_interface}}{}}
\newcommand{\pkgrun}{{\tt yggrun}}
\newcommand{\A}{Appendix{ }}
\newcommand{\hrefgit}[1]{\href{https://github.com/cropsinsilico/yggdrasil}{\todo{#1}}}
\newcommand{\hrefdoc}[1]{\href{https://cropsinsilico.github.io/yggdrasil/}{\todo{#1}}}
\newcommand{\hrefhack}[1]{\href{https://cropsinsilico.github.io/yggdrasil/hackathon2018/index.html}{\todo{#1}}}

@@

We present an Open Source Python package, {\pkg}, for creating and running integration networks by connecting existing computational models written in different programming languages. {\pkg} was developed as part of the Crops \emph{in Silico} \citep{Marshall-Colon2017} initiative to build a complete crop \emph{in silico} from the level of the genes to the level of the field. {\pkg} is available on Github\footnote{{\tt https://github.com/cropsinsilico/\pkglink}} with full documentation\footnote{{\tt https://cropsinsilico.github.io/\pkglink/}} and can be installed from PyPI\footnote{{\tt https://pypi.org/project/\pkglink/}} via {\tt pip install {\pippkg}} or conda-forge\footnote{{\tt https://github.com/conda-forge/\pkglink-feedstock}} via {\tt conda -c conda-forge install {\condapkg}}. Although developed for the purpose of integrating plant biology models, {\pkg} can be applied to any situation requiring coordination between models in the supported languages. \S\ref{S:background} provides background information on existing efforts for cross-language model integration, \S\ref{S:methods} describes the methods used by the {\pkg} package to integrate models, \S\ref{S:example} provides a worked example of integrating the two model presented above, \S\ref{S:results} presents several tests demonstrating the performance of message passing between integrated models, and \S\ref{S:discuss} describes a few use cases for {\pkg}, 
summarizes the features and limitations of the {\pkg} package, and outlines areas of ongoing and future development.
